---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggspeciesaccumulation

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ggspeciesaccumulation)](https://CRAN.R-project.org/package=ggspeciesaccumulation)
<!-- badges: end -->

ggspeciesaccumulation provides a ggplot2 stat for creating species accumulation curves on tidy dataframes. It works on occurrence data from places like [GBIF](https://www.gbif.org/) and [iNaturalist](https://www.inaturalist.org/). 

## Installation

You can install the development version of ggspeciesaccumulation like this:

``` r
# install.packages("pak")
pak::pak("pandionlabs/ggspeciesaccumulation")
```

## Example

Prepare a sample dataframe like this:

```{r example}
library(ggspeciesaccumulation)

 df <-
 tibble::tibble(
   speciesKey = runif(1000, 0, 300) |>
     round()
 )
 
```

Then use stat_species_acc() like this. Remember to specify the `species_key` aesthetic. `species_key` should be the column in your dataframe that denotes which species each observation record is. 

```{r}
ggplot2::ggplot(df, ggplot2::aes(species_key = speciesKey)) +
   stat_species_acc() +
   ggplot2::labs(y = "Species", x = "Observations")
```

You can use the normal ggplot aesthetics too!

```{r}
 df <-
 tibble::tibble(
   speciesKey = c(
     runif(1000, 0, 300) |> round(),  
     runif(1000, 0, 150) |> round()
     ),
   region = c(
     rep.int(1, 1000) |> factor(),
     rep.int(2, 1000) |> factor()
   )
 )
 
 ggplot2::ggplot(df, ggplot2::aes(species_key = speciesKey, colour = region)) +
   stat_species_acc(geom = "smooth") +
   ggplot2::labs(y = "Species", x = "Observations")
```

## Code of Conduct

Please note that the ggspeciesaccumulation project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
